Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-01-24 WSSSPE1_report/WSSSPE1_summary_report.tex
Fix unreadable characters around email addresses.

The workshop organizers:
\begin{itemize}
\item Daniel S. Katz <dkatz@nsf.gov>
\item Gabrielle Allen <gdallen@illinois.edu>
\item Neil Chue Hong <N.ChueHong@software.ac.uk>
\item Manish Parashar <parashar@rutgers.edu>
\item David Proctor <dproctor@nsf.gov>
\end{itemize}

Additional volunteers:
\begin{itemize}
\item Chris Mattmann <chris.a.mattmann@jpl.nasa.gov>
\item Ketan Maheshwari <ketancmaheshwari@gmail.com>
\item Marlon Pierce <marpierc@iu.edu>
\item Colin Venters <C.Venters@hud.ac.uk>
\item Suresh Marru <smarru@iu.edu>
\item Lynn Zentner <lzentner@purdue.edu>
\item Anne Elster <anne.elster@gmail.com>
\item Shel Swenson <mdswenso@usc.edu>
\item Andy Ray Terrel <andy.terrel@gmail.com>
\item Abani Patra <abani.patra@gmail.com>
\item Nancy Wilkins-Diehr <wilkinsn@sdsc.edu>
\item James Spencer <j.spencer@imperial.ac.uk>
\item Frank Loeffler <knarf@cct.lsu.edu>
\item James Hetherington <j.hetherington@ucl.ac.uk>
\item Sou-Cheng (Terrya) Choi <sou.cheng.terrya.choi@gmail.com>
\item James Howison <james@howison.name>
\item Bruce Berriman <gbb@ipac.caltech.edu>
\item Hilmar Lapp <hlapp@nescent.org>
\item Marcus D. Hanwell <marcus.hanwell@kitware.com>
\item Lucas Nussbaum <lucas.nussbaum@loria.fr>
\item Matthew Turk <matthewturk@gmail.com>
\end{itemize}

>>>>

The workshop organizers:
\begin{itemize}
\item Daniel S. Katz $\langle$\url{dkatz@nsf.gov}$\rangle$
\item Gabrielle Allen $\langle$\url{gdallen@illinois.edu}$\rangle$
\item Neil Chue Hong $\langle$\url{N.ChueHong@software.ac.uk}$\rangle$
\item Manish Parashar $\langle$\url{parashar@rutgers.edu}$\rangle$
\item David Proctor $\langle$\url{dproctor@nsf.gov}$\rangle$
\end{itemize}

Additional volunteers:
\begin{itemize}
\item Chris Mattmann $\langle$\url{chris.a.mattmann@jpl.nasa.gov}$\rangle$
\item Ketan Maheshwari $\langle$\url{ketancmaheshwari@gmail.com}$\rangle$
\item Marlon Pierce $\langle$\url{marpierc@iu.edu}$\rangle$
\item Colin Venters $\langle$\url{C.Venters@hud.ac.uk}$\rangle$
\item Suresh Marru $\langle$\url{smarru@iu.edu}$\rangle$
\item Lynn Zentner $\langle$\url{lzentner@purdue.edu}$\rangle$
\item Anne Elster $\langle$\url{anne.elster@gmail.com}$\rangle$
\item Shel Swenson $\langle$\url{mdswenso@usc.edu}$\rangle$
\item Andy Ray Terrel $\langle$\url{andy.terrel@gmail.com}$\rangle$
\item Abani Patra $\langle$\url{abani.patra@gmail.com}$\rangle$
\item Nancy Wilkins-Diehr $\langle$\url{wilkinsn@sdsc.edu}$\rangle$
\item James Spencer $\langle$\url{j.spencer@imperial.ac.uk}$\rangle$
\item Frank Loeffler $\langle$\url{knarf@cct.lsu.edu}$\rangle$
\item James Hetherington $\langle$\url{j.hetherington@ucl.ac.uk}$\rangle$
\item Sou-Cheng (Terrya) Choi $\langle$\url{sou.cheng.terrya.choi@gmail.com}$\rangle$
\item James Howison $\langle$\url{james@howison.name}$\rangle$
\item Bruce Berriman $\langle$\url{gbb@ipac.caltech.edu}$\rangle$
\item Hilmar Lapp $\langle$\url{hlapp@nescent.org}$\rangle$
\item Marcus D. Hanwell $\langle$\url{marcus.hanwell@kitware.com}$\rangle$
\item Lucas Nussbaum $\langle$\url{lucas.nussbaum@loria.fr}$\rangle$
\item Matthew Turk $\langle$\url{matthewturk@gmail.com}$\rangle$
\end{itemize}
